\begin{thebibliography}{99}

\bibitem{gallager1962}
R.~G. Gallager,
``Low-density parity-check codes,''
\textit{IRE Trans. Inf. Theory}, vol.~8, no.~1, pp.~21--28, Jan.~1962.

\bibitem{arikan2009}
E.~Ar\i kan,
``Channel polarization: A method for constructing capacity-achieving codes for
symmetric binary-input memoryless channels,''
\textit{IEEE Trans. Inf. Theory}, vol.~55, no.~7, pp.~3051--3073, Jul.~2009.

\bibitem{shor1995}
P.~W. Shor,
``Scheme for reducing decoherence in quantum computer memory,''
\textit{Phys. Rev. A}, vol.~52, no.~4, pp.~R2493--R2496, 1995.

\bibitem{fowler2012}
A.~G. Fowler, M.~Martinis, J.~M. Martinis, and J.~M. Gambetta,
``Surface codes: Towards practical large-scale quantum computation,''
\textit{Phys. Rev. A}, vol.~86, no.~3, p.~032324, 2012.

\bibitem{richardson2001}
T.~J. Richardson and R.~L. Urbanke,
``The capacity of low-density parity-check codes under message-passing decoding,''
\textit{IEEE Trans. Inf. Theory}, vol.~47, no.~2, pp.~599--618, Feb.~2001.

\bibitem{tal2013}
I.~Tal and A.~Vardy,
``List decoding of polar codes,''
\textit{IEEE Trans. Inf. Theory}, vol.~61, no.~5, pp.~2213--2226, May~2015.

\bibitem{lu2021}
L.~Lu, P.~Jin, G.~Pang, Z.~Zhang, and G.~E. Karniadakis,
``Learning nonlinear operators via DeepONet based on the universal approximation
theorem of operators,''
\textit{Nat. Mach. Intell.}, vol.~3, no.~3, pp.~218--229, Mar.~2021.

\bibitem{kovachki2023}
N.~Kovachki \textit{et al.},
``Neural operator: Learning maps between function spaces with applications to PDEs,''
\textit{J. Mach. Learn. Res.}, vol.~24, no.~89, pp.~1--97, 2023.

\bibitem{chen1995}
T.~Chen and H.~Chen,
``Universal approximation to nonlinear operators by neural networks with arbitrary
activation functions and its application to dynamical systems,''
\textit{IEEE Trans. Neural Netw.}, vol.~6, no.~4, pp.~911--917, Jul.~1995.

\bibitem{nachmani2018}
E.~Nachmani, E.~Marciano, L.~Lugosch, W.~J. Gross, D.~Burshtein, and Y.~Be'ery,
``Deep learning methods for improved decoding of linear codes,''
\textit{IEEE J. Sel. Topics Signal Process.}, vol.~12, no.~1, pp.~119--131, 2018.

\bibitem{nachmani2019}
E.~Nachmani and Y.~Be'ery,
``Hyper-graph-network decoders for block codes,''
in \textit{Proc. NeurIPS}, 2019, pp.~2329--2339.

\bibitem{kang2022}
M.~Kang \textit{et al.},
``Polar code design for generalized polar decoding,''
\textit{IEEE Trans. Commun.}, vol.~70, no.~11, pp.~7108--7122, Nov.~2022.

\bibitem{liu2023}
S.~Liu, W.~Fang, Y.~Li, Y.~Zhuo, J.~Li, and T.~Shi,
``RTLCoder: Outperforming GPT-3.5 in design RTL generation with our open-source
dataset and lightweight solution,''
\textit{arXiv preprint}, arXiv:2312.08617, 2023.

\bibitem{chang2024}
C.-H. Chang, Y.-M. Yang, C.-C. Ho, Y.-K. Wang, and H.-Y. Chang,
``Data is all you need: Finetuning LLMs for chip design via an automated design-data
augmentation framework,''
in \textit{Proc. DAC}, 2024.

\bibitem{ustun2020}
E.~Ustun, C.~Deng, D.~Pal, Z.~Li, and Z.~Zhang,
``Accurate operation delay prediction for FPGA HLS using graph neural networks,''
in \textit{Proc. ICCAD}, 2020, pp.~1--9.

\bibitem{geng2021}
H.~Geng \textit{et al.},
``N-Parity: A machine learning approach for estimating power and area of a neural
network VLSI implementation,''
in \textit{Proc. DATE}, 2021.

\bibitem{ryan2009}
W.~E. Ryan and S.~Lin,
\textit{Channel Codes: Classical and Modern}.
Cambridge, U.K.: Cambridge Univ. Press, 2009.

\bibitem{lin2004}
S.~Lin and D.~J. Costello,
\textit{Error Control Coding}, 2nd~ed.
Upper Saddle River, NJ: Prentice-Hall, 2004.

\bibitem{3gpp38212}
3GPP,
``NR; multiplexing and channel coding (Release 17),''
3GPP TS 38.212 v17.3.0, Sep.~2022.

\bibitem{velickovic2018}
P.~Veli\v{c}kovi\'{c}, G.~Cucurull, A.~Casanova, A.~Romero, P.~Li\`{o}, and Y.~Bengio,
``Graph attention networks,''
in \textit{Proc. ICLR}, 2018.

\bibitem{dwivedi2021}
V.~P. Dwivedi and X.~Bresson,
``A generalization of transformers to graphs,''
\textit{arXiv preprint}, arXiv:2012.09699, 2021.

\bibitem{li2021fno}
Z.~Li, N.~Kovachki, K.~Azizzadenesheli, B.~Liu, K.~Bhattacharya, A.~Stuart, and A.~Anandkumar,
``Fourier neural operator for parametric partial differential equations,''
in \textit{Proc. ICLR}, 2021.

\bibitem{gruber2017}
T.~Gruber, S.~Cammerer, J.~Hoydis, and S.~ten Brink,
``On deep learning-based channel decoding,''
in \textit{Proc. CISS}, 2017.

\bibitem{cammerer2022}
S.~Cammerer, M.~Schmalen, L.~Schmalen, and S.~ten Brink,
``Learned factor graphs for inference from stationary time sequences,''
\textit{IEEE Trans. Signal Process.}, vol.~70, pp.~366--381, 2022.

\bibitem{zhao2023}
Z.~Zhao, D.~Fan, and Z.~Xu,
``Neural network-based turbo equalization for memristive channels,''
\textit{IEEE Trans. Commun.}, vol.~71, no.~4, pp.~2098--2112, Apr.~2023.

\bibitem{preskill2018}
J.~Preskill,
``Quantum computing in the NISQ era and beyond,''
\textit{Quantum}, vol.~2, p.~79, 2018.

\bibitem{gottesman1997}
D.~Gottesman,
``Stabilizer codes and quantum error correction,''
Ph.D. dissertation, Caltech, 1997.

\bibitem{wang2023}
L.~Wang \textit{et al.},
``Large language model-assisted EDA flow for accelerating circuit design,''
in \textit{Proc. ICCAD}, 2023.

\bibitem{touvron2023}
H.~Touvron \textit{et al.},
``Llama 2: Open foundation and fine-tuned chat models,''
\textit{arXiv preprint}, arXiv:2307.09288, 2023.

\bibitem{brown2020}
T.~B. Brown \textit{et al.},
``Language models are few-shot learners,''
in \textit{Proc. NeurIPS}, 2020, pp.~1877--1901.

\bibitem{hu2021}
E.~J. Hu \textit{et al.},
``LoRA: Low-rank adaptation of large language models,''
in \textit{Proc. ICLR}, 2022.

\end{thebibliography}